\theseminartitle \\ \small \thetitle

### 2021-09-27 tex/paper.tex
Minor fixes for citations

\paragraph{Relevance} For a benchmark to be meaningful it is important that it, at least to a certain extent, reproduces some scenarios with real world application. This is what the "Relevance" of a benchmark refers to. It tries to define how relevant the produced information is to a potential user of a software. According to Kistowski et al. this makes it "perhaps the most important characteristic" (\cite{kistowski2015} p. 334). However the relevance of a benchmark may also limits the benchmarks applicability meaning, that a highly relevant benchmark for a specific system or component might only narrow applicability while benchmarks with a broad applicability will have a lower relevance but for a wider selection of applications. Kistowski et al. further elaborate on this with specific examples (\cite{kitowski2015} p. 334f)

@@

	Similar to \gls{cd} approaches in \gls{cb} the question also arises when to run the \gls{cb}. For \gls{cd}, optimally all tests and operations should be performed after every commit. However in practice this might not always be feasible due to the amount of tests and the associated compute time with that which is why complex software systems often alrady use a multi-tiered approach to \gls{cb}. A similar question arises when deciding on when to run \gls{cb}. Running benchmarks after every commit can pose challenges which will be further evaulated in \autoref{sssec:cb_challenges}. However for this paper our main focus will not be on when to run \gls{cb} but rather how the data produced by a \gls{cb} can be used to detect performance changes.

		\subsubsection{Opportunities and Challenges}

>>>>

\paragraph{Relevance} For a benchmark to be meaningful it is important that it, at least to a certain extent, reproduces some scenarios with real world application. This is what the "Relevance" of a benchmark refers to. It tries to define how relevant the produced information is to a potential user of a software. According to Kistowski et al. this makes it "perhaps the most important characteristic" (\cite{kistowski2015} p. 334). However the relevance of a benchmark may also limits the benchmarks applicability meaning, that a highly relevant benchmark for a specific system or component might only narrow applicability while benchmarks with a broad applicability will have a lower relevance but for a wider selection of applications. Kistowski et al. further elaborate on this with specific examples (\cite{kistowski2015} p. 334f)

@@

	Similar to \gls{cd} approaches in \gls{cb} the question also arises when to run the \gls{cb}. For \gls{cd}, optimally all tests and operations should be performed after every commit. However in practice this might not always be feasible due to the amount of tests and the associated compute time with that which is why complex software systems often alrady use a multi-tiered approach to \gls{cb}. A similar question arises when deciding on when to run \gls{cb}. Running benchmarks after every commit can pose challenges which will be further evaulated in the following section. However for this paper our main focus will not be on when to run \gls{cb} but rather how the data produced by a \gls{cb} can be used to detect performance changes.

		\subsubsection{Opportunities and Challenges}
		\label{sssec:cd_challenges}
